Designing a Search for the BBC

### 2014-02-12 paper.tex
Corrected citation.

\subsection{Objectives}

@@

Dogan and Henshaw\citep{dogan2010conceptual}
showed how a ‘soft’ systems approach called Interactive
Management can be adopted to capture the requirements and contextualise the
problem space. This involved the process of transitioning from the soft systems
results to a formal model (e.g. UML). This transition was enabled by dividing
the actors in the rich pictures into meta-level and direct users of the system.
Although this division was subjective and depended on the interpretation  and
analysis of the rich pictures to provide a structure for the use case model,
the rich pictures themselves were created through interactions with subject
matter experts. The soft systems, and hence the Interactive Management results,
provided the baseline information to derive a formal model including UML use
case, sequence and domain models. The transitioning from ``soft'' to ``hard''
systems can be set within the State of the Art including the requirements
analysis and modelling as used in SSM, UML and Business Process Modelling.

>>>>

\subsection{Objectives and Literative Review}

@@

Dogan and Henshaw\citep{dogan2010transition}
showed how a ‘soft’ systems approach called Interactive
Management can be adopted to capture the requirements and contextualise the
problem space. This involved the process of transitioning from the soft systems
results to a formal model (e.g. UML). This transition was enabled by dividing
the actors in the rich pictures into meta-level and direct users of the system.
Although this division was subjective and depended on the interpretation  and
analysis of the rich pictures to provide a structure for the use case model,
the rich pictures themselves were created through interactions with subject
matter experts. The soft systems, and hence the Interactive Management results,
provided the baseline information to derive a formal model including UML use
case, sequence and domain models. The transitioning from ``soft'' to ``hard''
systems can be set within the State of the Art including the requirements
analysis and modelling as used in SSM, UML and Business Process Modelling.
